---
title: "Base sample is not safe"
author: Mossa Merhi Reimert
output: 
  rmarkdown::html_vignette:
    df_print: tibble
vignette: >
  %\VignetteIndexEntry{Base sample is not safe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rbatteries)
```

For the most part, `sample()` does the job very well. Given some vector, we can
resample with replacement rather conveniently

```{r}
x <- 1:10
sample(x, replace = TRUE)
```

But what if the vector `x` is of size one?

```{r}
x <- 42
sample(x, replace=TRUE)
```

Suddenly the interpretation becomes sample from 1 to and including 42.

Looking in the documentation of `sample`

```{r}
if (length(x) == 1L && is.numeric(x) && is.finite(x) && 
    x >= 1) {
  # if (missing(size)) # missing is not available outside of function decl.
  #   size <- x
  size <- x # replaced with this 
  sample.int(x, size, replace = TRUE) 
}
```

This behaviour is documented in the details section of the help page of `sample`.

Resample on the other hand behave more intuitively.

```{r}
resample(x, replace = TRUE)
```

- [x] A unit-test is warranted here, as to ensure that `resample` always
      behaves like this.

## Resample for upsampling and downsampling

```{r, error=TRUE}
x <- 1:5
resample(x, n = 10)
```

This does not work, as the `n` in `sample.int` is present.

- [x] Change `resample` using `missing()` and also add a unit-test for this.

Upsampling results in a `NA` whenever `replace = FALSE` as well. This is not
meaningful. There are two ways to solve this 

- Default to `replace = TRUE` whenever `n >= length(x)`
- Throw a warning

It is not straightforward to change, because what if the user of `resample` calls
it with `replace = FALSE` and `n >= length(x)`? A warning seems like the best
procedure forward. 

- [x] Make a unit-test that expects a warning whenever `replace = FALSE` and 
`n >= length(x)`. 


## Resampling datasets

It is custom to have the rows of a data-frame denote the observations, and the
column corresponds to variables [^regressors].

[^regressors]: Also called regressors, features, and of course covariates. 

Take the `iris`-dataset as an example. It contains `r nrow(iris)` observations,
and say we want to downsample to three rows -- for whatever reason.

```{r}
resample(iris, n = 3)
```

This is not the expected result. The reason is, we are resampling along the first
dimension, which the one designated to variables, and not observations.

Here we have multiple ways of tackling this issue.

- [x] Make `resample` a generic, with specific behaviour for data-frames.
- Somehow default the selection of any other existing axis to be "all".
- Throw a warning whenever `x` is of non-vector type.


A possible scenario: One-column `data.frame` that we wish to `resample`, e.g.

```{r}
sepal_length_10 <- resample(iris$Sepal.Length, n = 10)
sepal_length_10
class(sepal_length_10)
```

- [x] Make a unit-test that ensures that this yields a `data.frame`, with one column named `Sepal.Length`.



Upsampling results in a `NA` whenever `replace = FALSE` as well. This is not
meaningful. There are two ways to solve this 

- Default to `replace = TRUE` whenever `n >= length(x)`
- Throw a warning

It is not straightforward to change, because what if the user of `resample` calls
it with `replace = FALSE` and `n >= length(x)`? A warning seems like the best
procedure forward. 

- [ ] Make a unit-test that expects a warning whenever `replace = FALSE` and 
`n >= length(x)`. 
