---
title: "Base sample is not safe"
author: Mossa Merhi Reimert
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Base sample is not safe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rbatteries)
```

For the most part, `sample()` does the job very well. Given some vector, we can
resample with replacement rather conveniently

```{r}
x <- 1:10
sample(x, replace = TRUE)
```

But what if the vector `x` is of size one?

```{r}
x <- 42
sample(x, replace=TRUE)
```

Suddenly the interpretation becomes sample from 1 to and including 42.

Looking in the documentation of `sample`

```{r}
if (length(x) == 1L && is.numeric(x) && is.finite(x) && 
    x >= 1) {
  # if (missing(size)) # missing is not available outside of function decl.
  #   size <- x
  size <- x # replaced with this 
  sample.int(x, size, replace = TRUE) 
}
```

This behavior is documented in the details section of the help page of `sample`.

Resample on the other hand behave more intuitively.

```{r}
resample(x, replace = TRUE)
```

- [x] A unit-test is warranted here, as to ensure that `resample` always
      behaves like this.

## What about up- and down-sampling?

```{r, error=TRUE}
x <- 1:5
resample(x, n = 10)
```

This does not work, as the `n` in `sample.int` is preset.

- [ ] Change `resample` using `missing()` and also add a unit-test for this.

